### 2020-06-17 text/article_vedrovice.Rmd
continue spatial analysis

Overall structure of the burial ground is examined using both density based approach,
and distance based methods [@osullivan2010, 121-154].
The density of burials is examined using quadrat test and the $G$ function while
the distance between neighbours usnig Ripley's $K$ function and its derivative, the
$L$ function [@ripley1976].
Given statistics for independent random process are estimated using Monte Carlo simulation
with 99 iterations and the most extreme results for each of the statistics
are used to construct envelopes encompassing the expected ranges

```{r spat-gl, fig.cap = "G and L functions"}
knitr::include_graphics(here("plots", "pointprocess_gl.pdf"))
```

@@

>>>>

Overall structure of the burial ground is examined using both density based approach
and distance based methods [@osullivan2010, 121-154].
The density of burials is examined using quadrat test while
the distance between neighbours using the $G$, Ripley's $K$ [@ripley1976] and $L$ functions.

The quadrat test divides the area of interest into several cells of fixed sizes
(quadrats) and compares the count of events per quadrat with the count
expected under the null hypothesis that the underlying point process
is completely spatially random (approximated by a Poisson distribution).
The $G$ function is a metric of how close events are and summarises
cummulative frequency distribution of the nearest neighbour distances.
Because of its dependence on the intensity of events in the study area, it is
subject to changes in the size of the study area.
Ripley's $K$ function (and variance stabilized $L$ function) is more resilient
to these changes and is widely used in archaeology [cf. @negre2018].

Given statistics for independent random process are estimated using Monte Carlo simulation
with 99 iterations and the most extreme results for each of the statistics
are used to construct envelopes encompassing the expected ranges

@@

```{r spat-gl, fig.cap = "G and L functions"}
knitr::include_graphics(here("plots", "pointprocess_fun.pdf"))
```
